\section{Appendix A: Model Context Summary (Mandatory)}

\textbf{This document is required for all models referenced in investment decisions, approval materials, or capital allocation discussions.} Models without a completed and approved Model Context Summary may not be used.

\subsection{Model Identification}

\begin{itemize}
  \item \textbf{Model ID:}
  \item \textbf{Model Name:}
  \item \textbf{Model Classification:} \(\square\) Diagnostic \(\square\) Translational \(\square\) Deployable
  \item \textbf{Lifecycle Status:} \(\square\) Research \(\square\) Approved \(\square\) Restricted \(\square\) Retired
  \item \textbf{Model Owner:}
  \item \textbf{Governance Reviewer:}
  \item \textbf{Associated Portfolio / Desk:}
\end{itemize}

\subsection{Intended Use}

\textbf{Primary Decision Supported}\\
(Describe the specific decision this model informs.)

\begin{quote}
Example: portfolio ranking for monthly rebalance within an equity factor sleeve.
\end{quote}

\textbf{Explicitly Excluded Uses}\\
(List decisions this model must not support.)

\begin{quote}
Example: intraday execution timing; discretionary override justification.
\end{quote}

\subsection{Declared Operating Context}

This section defines the conditions under which model outputs are considered valid.

\textbf{Asset Universe}

\begin{itemize}
  \item Instruments / markets covered:
  \item Inclusion / exclusion criteria:
\end{itemize}

\textbf{Data Inputs}

\begin{itemize}
  \item Data sources:
  \item Frequency and aggregation:
  \item Key preprocessing steps:
\end{itemize}

\textbf{Decision Horizon}

\begin{itemize}
  \item Signal horizon:
  \item Trading / rebalancing horizon:
\end{itemize}

\textbf{Portfolio Construction \& Execution}

\begin{itemize}
  \item Position sizing rules:
  \item Rebalancing frequency:
  \item Execution assumptions:
\end{itemize}

\textbf{Transaction Costs \& Market Impact}

\begin{itemize}
  \item Cost model used:
  \item Slippage / impact assumptions:
\end{itemize}

\textbf{Risk Constraints}

\begin{itemize}
  \item Exposure limits:
  \item Risk metrics enforced:
\end{itemize}

\textbf{Capacity \& Scale}

\begin{itemize}
  \item Capital levels evaluated:
  \item Known or expected capacity limits:
\end{itemize}

\subsection{Evaluation and Evidence Summary}

\textbf{Evaluation Design}\\
(Summarize how the model was evaluated in a manner consistent with the Operating Context.)

\textbf{Key Metrics Reviewed}\\
(List metrics actually used to support approval.)

\begin{quote}
Example: net returns after costs, turnover, drawdown, stability measures.
\end{quote}

\textbf{Trade-Offs Observed}\\
(Describe the principal trade-offs identified.)

\begin{quote}
Example: improved ranking sharpness coincides with higher turnover.
\end{quote}

\subsection{Assumptions and Fragilities}

\textbf{Key Assumptions}\\
(List assumptions that materially affect conclusions.)

\begin{quote}
Example: transaction costs \(\leq\) 10 bps one-way; monthly rebalance discipline.
\end{quote}

\textbf{Known Fragilities}\\
(Describe where behavior degrades or becomes unstable.)

\begin{quote}
Example: performance deteriorates rapidly at higher turnover or shorter horizons.
\end{quote}

\subsection{Monitoring Expectations}

\textbf{Primary Monitoring Metrics}\\
(List metrics used to assess ongoing behavior.)

\textbf{Expected Ranges / Thresholds}\\
(Provide validated ranges.)

\textbf{Escalation Triggers}\\
(Define conditions requiring review or restriction.)

\subsection{Capital Allocation Controls (Deployable Models Only)}

\begin{itemize}
  \item \textbf{Initial Capital Limit:}
  \item \textbf{Scaling Conditions:}
  \item \textbf{Reduction / Suspension Triggers:}
\end{itemize}

\subsection{Change and Re-Approval Triggers}

Changes to any of the following require review and potential re-approval:

\begin{itemize}
  \item \(\square\) Asset universe
  \item \(\square\) Data inputs
  \item \(\square\) Horizon or rebalance frequency
  \item \(\square\) Portfolio construction rules
  \item \(\square\) Cost or liquidity assumptions
  \item \(\square\) Risk constraints
  \item \(\square\) Intended use
\end{itemize}

\subsection{Approvals}

\textbf{Model Owner Certification}\\
I certify that this summary accurately reflects the model and its evaluated context.

\begin{itemize}
  \item Name / Signature / Date:
\end{itemize}

\textbf{Governance Review}

\begin{itemize}
  \item Reviewer Name / Signature / Date:
\end{itemize}

\textbf{Deployment Approval (if applicable)}

\begin{itemize}
  \item Authority / Signature / Date:
\end{itemize}

\subsection{Governing Statement}

\begin{quote}
\textbf{This model may be used only within the context described above. Use outside this context constitutes a governance violation.}
\end{quote}
