\section{Policy Review, Exceptions, and Amendments}

\subsection{Policy Review and Maintenance}

This Model Governance Framework shall be reviewed periodically to ensure continued relevance and effectiveness.

\subsubsection{Review Frequency}

\begin{itemize}
  \item The framework shall be reviewed at least annually.
  \item Additional reviews may be initiated in response to:
  \begin{itemize}
    \item material changes in firm strategy;
    \item significant market structure changes;
    \item regulatory developments; or
    \item identified governance failures.
  \end{itemize}
\end{itemize}

\subsubsection{Review Responsibility}

The review is led by Risk Management in coordination with Research, Operations, and Compliance, as applicable.

Proposed updates must be documented and approved by senior management or the Investment Committee, as appropriate.

\subsection{Policy Exceptions}

\subsubsection{Principle on Exceptions}

Exceptions to this framework are discouraged and permitted only in exceptional circumstances.

No exception may be granted solely for reasons of performance, time pressure, or opportunity cost.

\subsubsection{Exception Approval}

Any exception must:

\begin{itemize}
  \item be documented in writing;
  \item specify the exact provisions being excepted;
  \item define scope, duration, and rationale; and
  \item receive approval from the Investment Committee or delegated authority.
\end{itemize}

Temporary exceptions must include a defined expiration date.

\subsubsection{Monitoring of Exceptions}

Models operating under an exception:

\begin{itemize}
  \item are subject to enhanced monitoring;
  \item may be subject to reduced capital limits; and
  \item must be reviewed upon expiration of the exception.
\end{itemize}

Exceptions may be withdrawn at any time if risk increases.

\subsection{Amendments to the Framework}

Amendments to this framework must:

\begin{itemize}
  \item preserve the core principles outlined in Section 1;
  \item not weaken controls through redefinition or ambiguity; and
  \item be approved through the same governance process as the original policy.
\end{itemize}

Amendments must be communicated clearly to all affected functions.

\subsection{Interpretation and Precedence}

In the event of ambiguity:

\begin{itemize}
  \item interpretations that impose \textbf{greater discipline} take precedence over permissive interpretations.
  \item where this framework conflicts with other firm policies, the more restrictive requirement applies.
\end{itemize}

\subsection{Effective Date and Adoption}

This framework becomes effective upon formal approval by senior management or the Investment Committee.

All models in use as of the effective date must be:

\begin{itemize}
  \item entered into the Model Registry;
  \item classified under Section 2; and
  \item brought into compliance within a defined transition period.
\end{itemize}

\subsection{Final Statement}

\begin{quote}
\textbf{This framework exists to ensure that judgment, not momentum, governs the use of quantitative models. It is designed to make limits explicit before markets do so implicitly.}
\end{quote}
